On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-22 ms-suppinfo.tex
Separate SuppMat into another document. Full reference list from read.bib

\documentclass[10pt,twoside]{article}

@@

\usepackage[]{natbib}
\bibliographystyle{mee}

\begin{document}

@@

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits. Thus we narrow our search to only cover these two main traits.

@@

In total we inspected the full text of 583 articles, including \citet{\Sexpr{paste(names(read_bib), collapse=",")}}.

>>>>

\documentclass[10pt,twoside]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\usepackage[]{natbib}
\bibliographystyle{mee}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits. Thus we narrow our search to only cover these two main traits.

@@

In total we inspected the full text of 583 articles, including \citet{Ackerly:1996vo,Adler:2014jw,Agren:1985kl,Agren:1988fc,Agren:1996gl,Agren:2003ee,Agren:2004el,Agyeman:1999ef,aiba_tree_1996,Aiba:1997ho,Aiba:2005gl,Aiba:2009ft,AlmeidaCortez:1999jn,AlvarezClare:2009ht,anekonda_selection_1996,Anonymous:kmGgY8eO,Antunez:2001gk,Arendonk:1994kv,arendt_adaptive_1997,Arnqvist:1995es,Atkin:1996ug,Atkin:1996uy,Atkin:1998in,Atkin:2006kx,augspurger_light_1984,Augspurger:1984ct,Baker:2004jy,baltzer_determinants_2007,baltzer_physiological_2007,BarajasMorales:1987vz,baraloto_differential_2006,baraloto_seed_2005,Baraloto:2005er,Baraloto:2010fd,barberis_gaps_2005,Barigah:1998bi,Barot:2014hb,Beckmann:2012hn,Bellingham:2004kd,bicknell_development_1982,Blackman:1951ux,Bloor:2003fa,Bohlman:2006eo,Bonal:2007kf,bond_tortoise_1989,Bond:2001ti,Bond:2003bb,Bond:2005gn,Bongers:1990jl,Boogaard:1996hz,Boot:1996ug,Borchert:1994kj,Borenstein:2009um,Boring:1981ic,Botkin:1972tk,Bouffier:2008do,Bowman:2005ds,Bowman:2013cb,Brink:2011hi,Broncano:1998ck,Brouillette:2014hq,Brown:1996ks,Bruhn:2000jz,Buckley:2006ga,Burns:1997jy,Butterfield:1993uc,Cai:2007ie,Cai:2007vs,Cai:2008tu,Callaway:1994kk,CamaraZapata:2003df,CamaraZapata:2004up,Canadell:2007ij,Carmona:2010kp,Carnicer:2013el,caspersen_how_2011,Castro:2008wq,CastroDiez:1998gz,CastroDiez:2003jd,CastroDiez:2006gv,CastroDiez:2006gva,Catoni:2014bs,Causton:1994bk,Cebrian:1994jo,Cernusak:2008ds,Chacon:2005kn,Chambers:2001uw,Chao:2008hg,Chapin:1980gz,Chapin:1989il,Chaturvedi:2011jx,Chaturvedi:2014ie,Chave:2006tu,Chave:2009iy,Chen:2014jt,Chiariello:1989bl,clark_assessing_1999,clark_life_1992,Clark:1994kx,Clark:1999ed,Cochard:2007bn,Coleman:1994hm,coley_resource_1985,Coley:1983hk,Coley:1988wq,Comas:2002wt,Comas:2004jz,Comas:2004jza,Condit:1993hd,connell_subcanopy_1997,Conover:2009gj,Coombe:1962kz,coomes_comparison_1998,coomes_effects_2007,coomes_greater_2009,Cordero:2003wk,cornelissen_generalities_1999,cornelissen_interactive_1996,cornelissen_seedling_1996,Cornelissen:1996hf,Cornelissen:1997fd,Cornelissen:1998ta,Cornelissen:1999fq,Cornelissen:2001jr,Cornelissen:2003gw,Cornelissen:2008ge,Cregg:1988te,curran_wood_2008,dalling_seed_2002,Dalling:2004gs,darling_evaluating_2012,davies_tree_2001,DeBell:1994ix,DeDeyn:2008hv,DeLucia:1989kj,Delucia:1998vz,doncaster_non-linear_2008,Durand:2001fh,Duval:2000dg,Dyer:2001jw,Easdale:2009gv,edwards_allometric_2012,Edwards:2014db,Ellison:1993fz,Emmanuel:2014cz,Enquist:2007ek,Erickson:1974el,Evans:1998ug,Falagas:2008gtb,Falster:2005bw,Falster:2011ii,Falster:2015,Falster:2015bd,fan_hydraulic_2012,Farnsworth:1995im,Farrar:1989wt,Farrar:1998wx,Fayolle:2012bx,Fenner:1999ev,Fetene:2001kc,finegan_diameter_1999,FitzJohn:2014cf,Fortunel:2014gz,Fujimoto:2006fg,Galmes:2005fa,Garnier:1991kp,Garnier:1992kn,Garnier:1995fc,Garnier:1997ba,Garnier:1997fi,Garnier:1998wm,Garnier:2001fk,Gibert:2013bo,gilbert_life_2006,Givnish:1995ta,gleeson_plant_1994,Goldberg:1982cf,GonzalezMunoz:2013ie,Goudriaan:1990tl,Gower:1993jo,Grattapaglia:1996tq,Gregorczyk:1996fv,Grime:1975gr,Grime:1975kk,Grime:1977kc,Grime:1997wm,Grime:2012gt,grime1979plant,Groninger:1996bu,grotkopp_toward_2002,Grotkopp:2007di,Grubb:1977ki,Grubb:1996kr,Grubb:1996kra,Gulias:2009ja,Gunatilleke:1997hd,Gusewell:2004kc,gutsell_accurately_2002,Hannrup:2004ke,Hattenschwiler:2001eu,HDBradshaw:1995tu,Hellgren:1996by,Hempson:2014ir,Herault:2010db,Herault:2011dd,Higgins:2002iq,Higgins:2003hz,Hilbert:1990vo,Hipps:1995tu,Hirose:1988jl,HOFFLAND:1996gk,Hoffmann:2003ga,Holzwarth:2015dg,Hoshika:2014gv,houghton_does_2013,Houter:2014gu,Huante:1992jg,Huante:1995fd,Huante:1995tl,Huante:1998bk,Huante:1998ft,Huante:1998hx,Hubbell:2005dm,Hummel:2006ko,Hunt:1987wc,HUNT:1997ge,HUNT:1997gf,Huxley:1967gk,Iida:2012jb,Iida:2014ep,Iida:2014hq,Imaji:2010ik,Ingestad:1979fi,Ingestad:1995kw,Ishii:2000et,Ivancich:2012iu,Jennions:2013ta,Johnson:2009iz,Jurado:1992fh,Karlsson:1987il,Ke:1999bk,Khurana:2004wv,Kidd:1921bp,king_correlations_1991,king_influence_1994,king_relationships_1997,king_size-related_2011,king_tree_2005,King:2006dg,King:2006he,Kitajima:1994ez,Kitajima:2002fm,Kitajima:2013hb,Kneeshaw:2006bd,kobe_carbohydrate_1997,Kobe:1999ha,Koch:2004br,Kohyama:2003dk,Konings:1989we,Koricheva:2013hy,Koricheva:2013tz,Koricheva:2014ku,Korner:2005dh,korning_growth_1994,Kraft:2008un,Kruger:2006fq,Kruger:2006fqb,Kumar:2014iz,Kunstler:2009dt,Kunstler:2010ei,Kwesiga:1986tk,Lachapelle:2012kl,Lacourse:2009wg,Lajeunesse:2013tm,Lamarque:2011im,Lambers:1992bj,Lambers:2004bj,Lamers:2006dl,Larjavaara:2010bn,Larjavaara:2014ur,Lasky:2013iq,Lasky:2015wu,Latham:1992ei,Lavorel:2002ff,Lavorel:2002tw,Leao:2014hw,Lee:1996bh,Leoni:2009jx,Li:2005ww,Li:2013bi,Limpens:2014cm,lind_life-history_2013,Loach:1970gp,loehle_height_1998,loehle_tree_1988,Loehle:1988je,Long:1996vp,Long:2011er,LopezIglesias:2014dk,Loveys:2002hj,Loveys:2003kl,Lu:2014kb,lusk_leaf_2002,lusk_leaf_2004,lusk_ontogenetic_2006,lusk_whole-plant_2013,Lusk:1997ga,Lusk:2002fm,Lusk:2002fma,Lusk:2008fo,Lusk:2011cf,Lusk:2013bq,Lusk:2013hz,MadrigalGonzalez:2014go,Maranon:1993iv,Markesteijn:2009if,Marron:2005cm,Martin:2011ij,MartinezVilalta:2010iq,Matias:2011fq,Mayfield:2006gn,McCormack:2012ch,mccormick_larval_2004,McIntyre:1999go,McMillin:1973iv,Mediavilla:2003cg,Meinzer:2011br,Menaut:1990dl,MendesRodrigues:2011bc,Metcalfe:1997jy,Meziane:1999ci,Milberg:1998hv,Moles:2006ft,Montgomery:2004wq,Mooney:1978dl,Morin:2011ih,Moya:2008ep,Muller-landau_interspecific_2004,Muller:1990di,MullerLandau:2004dc,MullerLandau:2008eo,Mundim:2012eo,MunneBosch:2004ki,Murphy:1986vw,Murray:2013hd,MYERS:2007fo,myster_tree_2009,Nascimento:2005kl,Niemann:1995by,Niinemets:1999tw,Niinemets:2006jy,Niklas:2010bd,Nikula:2011ke,Norby:1989jc,Norby:2001go,OBERBAUER:1986ib,OKALI:1972uf,Oren:1986he,Osada:2001cq,Osada:2011ds,Osone:2008dr,Osone:2014hb,Osunkoya:1991en,Osunkoya:1994ip,Osunkoya:2010ef,Pages:2003ke,Paine:2015df,palik_vertical_1993,Paz:2005kx,Pere:2013gr,Pietsch:2014he,Piper:1986el,Pliura:2007we,POLLARD:1968wv,poorter_relationships_2008,Poorter:1986bb,Poorter:1989tx,Poorter:1990bt,Poorter:1990ku,Poorter:1991cf,Poorter:1991ki,Poorter:1992hg,Poorter:1994em,Poorter:1995jn,Poorter:1996kt,Poorter:1998uf,Poorter:1999fp,Poorter:1999wd,Poorter:2001fj,Poorter:2002uj,Poorter:2003dn,Poorter:2005dj,Poorter:2006kw,Poorter:2006vb,Poorter:2008iu,Poorter:2009ia,Poorter:2010co,Poorter:2012if,Popma:1988tv,PORTSMUTH:2007kn,Prentice:1991dz,primack_growth_1985,Prior:2004cv,Pugnaire:1999ww,Queenborough:2013jf,Quero:2008jg,Ralanguageanden:2014wf,Read:2011du,Reed:2003cx,Rees:2010gk,Reich:1987fh,Reich:1991kf,Reich:1992wm,Reich:1994bt,Reich:1995cb,Reich:1998ir,Reich:1998ja,Reich:1998ti,Reich:1998vb,Reich:1999gp,Reich:2003gm,Reich:2003jy,Reich:2014ho,Rice:1989ex,Rincon:1993cp,Rincon:1994da,Roderick:2000id,Rohula:2014cp,Rosenberg:2005hk,Rosenthal:1979do,Rossatto:2009gq,Rossi:2006ky,Roumet:1996jb,Rowland:2014bw,Rozendall:2006hm,Ruger:2011kv,Ruger:2012jv,Ruger:2012jva,RuizRobleto:2005hc,russo_interspecific_2008,Ryser:1996fo,Ryser:2014vo,Sack:2001ev,Sack:2004hm,Sack:2013ku,saldana-acosta_seedling_2009,SaldanaAcosta:2008jv,SalgadoLuarte:2010gg,SalgadoLuarte:2012ci,SanchezGomez:2006kg,Santiago:2004bn,Santiago:2007dw,Santiago:2007wi,Santos:2012gt,Saverimuttu:1996ih,Scheiter:2013ed,Schererlorenzen:2007ie,Schlapfer:1996fs,Scholes:1997vz,Schulze:2006ww,schumacher_influence_2009,Sellin:2013fi,Senevirathna:2003un,Shen:2014fw,Shinano:2001wr,Shipley:1990js,Shipley:2000jv,Shipley:2002ek,Shipley:2002fs,Shipley:2006dx,Shipley:2006ie,Sillett:2010ck,Soriano:2011ep,South:1991wn,Srivastava:2009we,stahl_whole-plant_2013,Stephenson:2014ek,sterck_plasticity_2013,sterck_sapling_2014,Sterck:2001ii,Sterck:2006wk,Sterck:2011eh,StGermain:2008fi,Stratton:2001ck,Sugiura:2011kc,Sugiyama:2005gx,Sungpalee:2009bh,Suzuki:1999id,svenning_seedling_2008,Swanborough:1996im,Swenson:2007iv,Swenson:2008ij,Syvertsen:1981uv,Tamme:2014wl,TanakaOda:2010dg,Taub:2002ku,Taylor:2001ur,terSteege:2001hy,Thomas:1996do,Thomas:1999bv,Thomas:2011br,Tjoelker:1998em,Tjoelker:1999gp,Tobner:2013cv,Tolley:1984ge,Tomlinson:2014im,Tullus:2012kw,turnbull_growth_2008,Turnbull:2012ew,Valentine:2012dz,Valio:2001tz,Valladares:2000bd,Valladares:2006bb,van_der_werf_importance_1998,van_dooren_delayed_1998,VanAndel:1989vq,vanderHeijden:2007kj,vanderWerf:1993by,VEENENDAAL:td,Veneklaas:1998uk,Veneklaas:2002dt,Venus:1979vd,Venus:1979wh,Vieira:2014cd,Vigl:2014hw,Villagra:2013do,Villar:1998iz,Villar:2006cf,VillarSalvador:2004th,Violle:2007jw,Vitasse:2009ke,Vogel:1988ux,Walczynska:2012hv,Wallentin:2008iw,WALTER:2008hc,walters_are_1996,walters_low-light_1999,Walters:1993eu,Walters:1993hf,Walters:2000tk,Wang:1998cs,Waring:1985ii,Warren:2005bc,Watling:1997ep,Watling:1997id,Weber:2008im,Weedon:2009ko,Weiher:1999js,West:2003fo,Westbrook:2011ja,Westoby:1998ug,Westoby:2002ft,Westoby:2006dm,Westoby:2009ch,Whale:1985to,White:2007gs,Wikberg:2004hl,Wikstrom:1995dc,Wilson:1999dm,Wright:1998ub,Wright:1999ds,Wright:1999eha,Wright:2000kw,Wright:2001gb,Wright:2003kb,Wright:2004jb,Wright:2005iv,Wright:2010tp,Xiong:2000hw,Xiong:2001ep,Xiong:2001es,Xu:2014cn,Yan:2008vk,Yang:1994cf,Yang:2010ek,Yang:2014js,yavitt_seedling_2008,Yeboah:2013jh,yetter_height_1986,Zhang:1995bh,Zhang:1995dz,Zhang:2011fe,Zvereva:2008jm}.
